\jaxcosmo: End-to-End Differentiable and GPU Accelerated Cosmology Library

### 2022-06-01 paper.tex
add refence to 2018PhRvD..98d3526A: Dark Energy Survey Year 1 Results: Cosmological Constraints from Galaxy Clustering and Weak Lensing

Then, using the \numpyro\ PPL, we have set up a \textit{forward model} using the prior description  Table \ref{tab-DESY1} as for instance the $\Omega_c$ parameter
\begin{minted}[fontsize=\footnotesize]{python}
Omega_c = numpyro.sample('Omega_c', Uniform(0.1, 0.9))
\end{minted}
Then, we generate mock angular power spectra $C_\ell$ from the auto \& cross correlations of the Number Counts and Weak Lensing probes computed with the \texttt{gaussian\_cl\_covariance\_and\_mean} function in the \texttt{jc.angular\_cl} module. One reads
\begin{minted}[fontsize=\footnotesize]{python}
# Define the lensing and number counts probe
    probes = [jc.probes.WeakLensing(nzs_s_sys, 
                                    ia_bias=b_ia,
                       multiplicative_bias=m),
             jc.probes.NumberCounts(nzs_l, b)]
cl, C = gaussian_cl_covariance_and_mean(cosmo, ell, probes, 
                               f_sky=0.25, sparse=True)
\end{minted} 
with \texttt{cosmo} an instance of the \texttt{jc.Cosmology} setting the cosmological parameters generated with the priors, and \texttt{ell} a series of 50 angular modes. The generation of the mock data yields from the possibility to execute a conditioned model with a fiducial cosmology, leaving \numpyro\ dealing with the random number generation:
\begin{minted}[fontsize=\footnotesize]{python}
fiducial_model = condition(model,
    {'Omega_c':0.2545, 'sigma8':0.801, 
    'h':0.682, 'Omega_b':0.0485, 'w0':-1.,'n_s':0.971,
     'A':0.5,'eta':0.,
     'm1':0.0,'m2':0.0,'m3':0.0,'m4':0.0,
     'dz1':0.0,'dz2':0.0,'dz3':0.0,'dz4':0.0,
     'b1':1.2,'b2':1.4,'b3':1.6,'b4':1.8,'b5':2.0
      })

>>>>

Then, using the \numpyro\ PPL, we have set up a \textit{forward model} following the reference \citep{2018PhRvD..98d3526A}. The prior descriptions of the different model parameters are described in Table \ref{tab-DESY1}.  For instance the $\Omega_c$ parameter is treated as random variable as followed
\begin{minted}[fontsize=\footnotesize]{python}
Omega_c = numpyro.sample('Omega_c', Uniform(0.1, 0.9))
\end{minted}
Then, we generate mock angular power spectra $C_\ell$ from the auto \& cross correlations of the Number Counts and Weak Lensing probes computed with the \texttt{gaussian\_cl\_covariance\_and\_mean} function in the \texttt{jc.angular\_cl} module. One reads
\begin{minted}[fontsize=\footnotesize]{python}
# Define the lensing and number counts probe
    probes = [jc.probes.WeakLensing(nzs_s_sys, 
                                    ia_bias=b_ia,
                       multiplicative_bias=m),
             jc.probes.NumberCounts(nzs_l, b)]
cl, C = gaussian_cl_covariance_and_mean(cosmo, ell, probes, 
                               f_sky=0.25, sparse=True)
\end{minted} 
with \texttt{cosmo} an instance of the \texttt{jc.Cosmology} setting the cosmological parameters generated with the priors, and \texttt{ell} a series of 50 angular modes. The generation of the mock data yields from the possibility to execute a conditioned model with a fiducial cosmology, leaving \numpyro\ dealing with the random number generation:
\begin{minted}[fontsize=\footnotesize]{python}
fiducial_model = condition(model,
    {'Omega_c':0.2545, 'sigma8':0.801, 
    'h':0.682, 'Omega_b':0.0485, 'w0':-1.,'n_s':0.971,
     'A':0.5,'eta':0.,
     'm1':0.0,'m2':0.0,'m3':0.0,'m4':0.0,
     'dz1':0.0,'dz2':0.0,'dz3':0.0,'dz4':0.0,
     'b1':1.2,'b2':1.4,'b3':1.6,'b4':1.8,'b5':2.0
      })
